A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Axis of evil

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:prettyheatmaps1,figure:prettyheatmaps2} we plot the number of
recursive calls made by our algorithm on the $y$-axis versus the number made by
CP-FC on the $x$-axis, for the unlabelled and labelled, unconnected problem
instances. (Rather than a simple scatter plot, we use darker colours to
indicate a higher density of points around a location.) We see a close
correlation: we typically do slightly less work, and sometimes do more, but
instances with more than one order of magnitude difference in search space size
are rare.

>>>>

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:prettyheatmaps1,figure:prettyheatmaps2} we plot the number of
recursive calls made by our algorithm versus the number made by
CP-FC, for the unlabelled and labelled, unconnected problem
instances. (Rather than a simple scatter plot, we use darker colours to
indicate a higher density of points around a location.) We see a close
correlation: we typically do slightly less work, and sometimes do more, but
instances with more than one order of magnitude difference in search space size
are rare.
